\input{common.tex}

\begin{document}

\puttitle{}

\section{Introduction}

These instructions explain the setup of a containerized environment for developing Zephyr applications.
This environment can either be used with a container runtime or the \emph{Windows Subsystem for Linux} (WSL).

The \emph{Containerfile} can be found in Appendix~\ref{containerfile} for anyone interested.

\input{native.tex}

\section{Technical Background (optional read)}

\subsection{Necessity for WSL or Containers}

In the following labs, you are going to work with the Zephyr RTOS.
By providing a containerized environment, we can ensure a reproducible setup.
Additionally, the images are lightweight, have a small memory footprint, and outperform a conventional VM.

\subsection{Windows Subsystem for Linux}

The Windows Subsystem for Linux (WSL 2) is available for Windows 10/11 since 2019.
Not all Windows Versions include it per default, an installation is possible via the Microsoft Store or \emph{winget}.
WSL 2 runs inside a managed virtual machine (VM) that includes a Linux kernel.
The virtualization is implemented via a highly optimized subset of Hyper-V features.
WSL 2 on Windows 11 can retain up to 95 \% of the performance of a native Linux Distribution.

\subsubsection*{Benefits compared to a conventional VM}

\begin{itemize}
  \item Seamless integration in Windows.
    Files contained within the WSL can be accessed directly via the regular Windows file explorer.
  \item After creating a WSL image, it can be started directly in the file explorer.
  \item The VM setup is seamless and executed automatically without user
    interaction.
\end{itemize}

\subsection{Container Runtime}
Container runtimes are an alternative to the VM that WSL 2 provides.
These runtimes are typically developed for linux systems\footnote{Docker and Podman are available for Windows but run in WSL 2 in the background}.
Two notable container runtimes are \emph{Docker} and \emph{Podman}.

\newpage

\input{wsl.tex}

\newpage

\input{container_runtime.tex}

\newpage

\input{using_env.tex}
\newpage
\input{test_sample.tex}

\newpage

\appendix

\fancyfoot{}

\input{vs_code.tex}

\section{Troubleshooting}

\input{troubleshooting.tex}

\subsection{Container}

\input{troubleshooting_container.tex}

\subsection{WSL}

\input{troubleshooting_wsl.tex}

\newpage
\newgeometry{margin=1cm}

\section{Containerfile}\label{containerfile}

\lstinputlisting[basicstyle=\ttfamily\scriptsize]{../Containerfile}

Usage example:

\begin{monobox}
podman build \
  --build-arg="ZEPHYR_VERSION=@\zephyrversion{}@" \
  --build-arg="SDK_VERSION=@\sdkversion{}@" \
  . -t @\imagename{}@
\end{monobox}

\end{document}
